(Re-)bridging the anatomy ontologies with SSSOM

### 2024-04-02 sssomt.tex
Typo fix.

One of the prerequisites for the reuse and renalysis of datasets from
high-throughput experimental methods --~such as single-cell RNA
sequencing datasets~-- beyond their lab of origin is the annotation of
samples and results with standardised terms. That is, we need controlled
vocabularies to properly record information such as the exact techniques
used, the organs or tissues from which the experimental samples were
taken, or the cell types that were identified. Several ontologies have
been developed for this kind of purpose, such as the Experimental Factor
Ontology (EFO) to annotate experimental methods~\cite{malone2010}, the
Drosophila Anatomy Ontology (FBbt) to annotate anatomical structures and
cell types in \species{D.~melanogaster}~\cite{costa2013}, the Worm
Anatomy Ontology (WBbt) to do the same in
\species{C.~elegans}~\cite{lee2003}, etc. Most of those ontologies are
grouped under the umbrella of the OBO Foundry~\cite{jackson2021}.

>>>>

One of the prerequisites for the reuse and reanalysis of datasets from
high-throughput experimental methods --~such as single-cell RNA
sequencing datasets~-- beyond their lab of origin is the annotation of
samples and results with standardised terms. That is, we need controlled
vocabularies to properly record information such as the exact techniques
used, the organs or tissues from which the experimental samples were
taken, or the cell types that were identified. Several ontologies have
been developed for this kind of purpose, such as the Experimental Factor
Ontology (EFO) to annotate experimental methods~\cite{malone2010}, the
Drosophila Anatomy Ontology (FBbt) to annotate anatomical structures and
cell types in \species{D.~melanogaster}~\cite{costa2013}, the Worm
Anatomy Ontology (WBbt) to do the same in
\species{C.~elegans}~\cite{lee2003}, etc. Most of those ontologies are
grouped under the umbrella of the OBO Foundry~\cite{jackson2021}.
